method

### 2021-11-12 06_Paper/ER-ED/method.Rmd
Update method.Rmd

```{r import, echo=FALSE, message=FALSE, warning=FALSE}

```

>>>>

```{r import, echo=FALSE, message=FALSE, warning=FALSE}
# import ER ratings and ER discounting data into lists

datalist_ER = lapply(list.files(here("04_RawData", "Pilot", "ER_ED"), pattern = '.*ER.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)

datalist_ED = lapply(list.files(here("04_RawData", "Pilot", "ER_ED"), pattern = '.*_ED.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)
```
